---
title: "How to use `rvolleydata`"
author: "Matthew Chow"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rvolleydata-how-to-use}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>"
)
```

## Overview

This vignette will outline how to use the functions in the `rvolleydata` package to access data from League One Volleyball Pro (LOVB), Athletes Unlimited Pro Volleyball (AUPVB), and Major League Volleyball (MLV) leagues.

```{r setup}
library(rvolleydata)
library(dplyr)
```

## Installation

You can install the development version of [**`rvolleydata`**](https://github.com/awosoga/rvolleydata) from [GitHub](https://github.com/awosoga/rvolleydata) with:

```{r installation, eval=FALSE}
# install.packages("devtools")
devtools::install_github("awosoga/rvolleydata")
```

## Usage

The following code snippets will provide information on how to access different volleyball league statistics. The structure of the functions is similar across League One Volleyball Pro (LOVB) and Major League Volleyball (MLV), so LOVB functions will be used as an example.

### Schedules

Use `load_lovb_schedule` to access League One Volleyball Pro (LOVB) schedules.

```{r schedule}
load_lovb_schedule <- load_lovb_schedule(2025)
glimpse(load_lovb_schedule)
```

### Player Info

Use `load_aupvb_player_info` to access Athletes Unlimited Pro Volleyball (AUPVB) player information.

```{r player_info}
load_aupvb_player_info <- load_aupvb_player_info(2024)
glimpse(load_aupvb_player_info)
```

### Leaderboards

Use `load_aupvb_leaderboards` to access Athletes Unlimited Pro Volleyball (AUPVB) leaderboards.

```{r leaderboards}
load_aupvb_leaderboards <- load_aupvb_leaderboards(2024)
glimpse(load_aupvb_leaderboards)
```

### Play-by-Play

Use `load_aupvb_pbp` to access Athletes Unlimited Pro Volleyball (AUPVB) play-by-play data.

```{r aupvb_pbp}
load_aupvb_pbp <- load_aupvb_pbp(2024)
glimpse(load_aupvb_pbp)
```

Use `load_lovb_pbp` to access League One Volleyball Pro (LOVB) play-by-play data.

```{r lovb_pbp}
load_lovb_pbp <- load_lovb_pbp(2025)
glimpse(load_lovb_pbp)
```

### Officials

Use `load_lovb_officials` to access League One Volleyball Pro (LOVB) officials data.

```{r officials}
load_lovb_officials <- load_lovb_officials(2025)
glimpse(load_lovb_officials)
```

### Player Information

Use `load_lovb_player_info` to access League One Volleyball Pro (LOVB) player information.

```{r boxscores}
load_lovb_player_info <- load_lovb_player_info(2025)
glimpse(load_lovb_player_info)
```

### Team Staff

Use `load_lovb_team_staff` to access League One Volleyball Pro (LOVB) team staff data.

```{r team_staff}
load_lovb_team_staff <- load_lovb_team_staff(2025)
glimpse(load_lovb_team_staff)
```

### Events Log

Use `load_lovb_events_log` to access League One Volleyball Pro (LOVB) events log data.

```{r events_log}
load_lovb_events_log <- load_lovb_events_log(2025)
glimpse(load_lovb_events_log)
```

### Player Boxscores

Use `load_lovb_player_boxscore` to access League One Volleyball Pro (LOVB) player boxscore data.

```{r player_boxscores}
load_lovb_player_boxscores <- load_lovb_player_boxscore(2025)
glimpse(load_lovb_player_boxscores)
```

### Team Boxscores

Use `load_lovb_team_boxscore` to access League One Volleyball Pro (LOVB) team boxscore data.

```{r team_boxscores}
load_lovb_team_boxscores <- load_lovb_team_boxscore(2025)
glimpse(load_lovb_team_boxscores)
```
